Estimation of carbon stocks in Colombian mangroves and associated uncertainties

### 2017-04-19 Article_mangroves.tex
Last changes before moving to different location
in supplementary information all models were updated and modification in methods in article

\begin{abstract}
We estimated carbon (C) stocks in aboveground biomass (AGB) for mangroves in the Caribbean and Pacific coasts of Colombia. Using available data on AGB density and mangrove area for the whole country and each coast independently, we estimated a national carbon stock in AGB for Colombian mangroves as 14.95 $\pm$ 2.72 TgC (mean $\pm$ SE), with 2.20 $\pm$ 0.86 TgC in the Caribbean coast and 9.61 $\pm$ 2.78 TgC in the Pacific coast. Uncertainty for total carbon in AGB in Colombian mangroves, reported as SE/mean in percentage, was 18\% at the national level, 39\% in the Caribbean coast, and 29\% in the Pacific coast. This uncertainty was more influenced by uncertainties associated with the estimation of mangrove area for the Caribbean coast, while for the Pacific coast it was more influenced by the uncertainties associated with AGB density. This difference is the result of a contrasting availability of AGB density data for both coasts.  Comparison between observed AGB density data and predictions from large-scale models showed that these models underestimate AGB density for Colombian mangroves. We reparameterized these models with our data, but found poor goodness-of-fit statistics for these model structures. We propose therefore four new statistical models to predict AGB density in Colombian mangroves based on climatic and vegetation data. In all cases, the best models included the enhanced vegetation index (EVI) and the mean temperature of driest quarter (BIO9). 
\end{abstract}

@@

\subsection {Carbon stock estimation using the predictive average model (SECCION PUEDE SER ELIMINADA SI NO SE PUEDE OBTENER EL MODISSummaries PARA LOS 2 MILLONES DE PUNTOS)}
We used the modavgPred function from AICcmodavg R Package to compute model-average predictions of biomass based on the entire candidate models set. Data base used for model-average predictions was built with coordinates of mangrove cover in Colombia related in Global Mangrove Forests Distribution, 2000 \citep{Giri2013, Giri2010}. Bioclimatic variables used in each chosen model as well as EVI data were obtained from WorldClim and LP DAAC data bases as was made for the data used for fitting models.  The uncertainty associated with the estimation was calculated. ESTO LO PODEMOS HACER SI TENEMOS EL MODISSummary PARA LOS 2 MILLONES DE PUNTOS.

Finally, we associated the estimated biomass with the mangrove area for Colombia calculated from \citet{Giri2013, Giri2010} data. We considered a conversion factor from biomass to carbon of 0.50, as is proposed by several authors \citep{MacDicken1997, Clark2001, Fearnside2004, Chave2005, Aragao2009}.

\subsection{Mapping ESTA SECCION SE DESARROLLA SI SE PUEDE OBTENER EL MODISSummaries}

The data with a spatial resolution of 30 m was used to build a national map of potential AGB. 
The data are available at 30-m spatial resolution

>>>>

\begin{abstract}
We estimated carbon (C) stocks in aboveground biomass (AGB) for mangroves in the Caribbean and Pacific coasts of Colombia. Using available data on AGB density and mangrove area for the whole country and each coast independently, we estimated a national carbon stock in AGB for Colombian mangroves as 14.95 $\pm$ 2.72 TgC (mean $\pm$ SE), with 2.20 $\pm$ 0.86 TgC in the Caribbean coast and 9.61 $\pm$ 2.78 TgC in the Pacific coast. Uncertainty for total carbon in AGB in Colombian mangroves, reported as SE/mean in percentage, was 18\% at the national level, 39\% in the Caribbean coast, and 29\% in the Pacific coast. This uncertainty was more influenced by uncertainties associated with the estimation of mangrove area for the Caribbean coast, while for the Pacific coast it was more influenced by the uncertainties associated with AGB density. This difference is the result of a contrasting availability of AGB density data for both coasts.  Comparison between observed AGB density data and predictions from large-scale models showed that these models underestimate AGB density for Colombian mangroves. We reparameterized these models with our data, but found poor goodness-of-fit statistics for these model structures. We propose therefore three new statistical models to predict AGB density in Colombian mangroves based on climatic and vegetation data. In all cases, the best models included the enhanced vegetation index (EVI) and the mean temperature of driest quarter (BIO9). 
\end{abstract}

@@

\subsection {AGB estimation using the predictive models}
We estimated model-average predictions of AGB based on the candidate models classified as ``substantial weight models'' category according to the results of the ``model selection table'' describe in the above section. Model-average predictions were carried out weighting each model by its AIC weight.

 EVI data base used for the estimation was got from ACA ES NECESARIO TENER CLARA LA FUENTE DE INFORMACIÓN DE VICTOR. For the same points associated with EVI data, we obtained the WorldClim bioclimatic variables BIO9 and BI016.

COMO ESTIMO LA INCERTIDUMBRE ASOCIADA A ESA ESTIMACIÓN?
